### 2017-06-20 paper.tex
Callout box with learner profile

@@

>>>>

% frames around boxes
\usepackage{mdframed}

@@

\begin{mdframed}

\noindent
Box 1: Learner Profile

Jorge has just moved from Costa Rica to Canada to study agricultural engineering.
Other than using Excel, Word, and the Internet,
Jorge's most significant previous experience with computers is
helping his sister build a WordPress site for the family business.

Jorge needs to measure properties of soil from nearby farms
using a handheld device that sends text files to his computer.
Right now, Jorge has to open each file in Excel,
crop the first and last points,
and calculate an average.
This workshop will show Jorge how to write a little Python program
to read the data,
select the right values from each file,
and calculate the required statistics.

\end{mdframed}
